### 2022-06-08 manuscript.tex
Merge pull request #221 from shafieisabets/main [ci skip]
This build is based on
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/c579f2e6dabd3334b02f563bb8ac53bfd042db72.

This commit was created by the following CI build and job:
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/c579f2e6dabd3334b02f563bb8ac53bfd042db72/checks
https://github.com/SORTEE-Github-Hackathon/manuscript/actions/runs/2463785278

This manuscript
(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/eafc396e1f32d378749c27716bfc058f4802928f/}{permalink})
was automatically generated
from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/eafc396e1f32d378749c27716bfc058f4802928f}{SORTEE-Github-Hackathon/manuscript@eafc396}
on June 8, 2022.

@@

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 0\tabcolsep) * \real{1.0000}}@{}}
\toprule
\begin{minipage}[b]{\linewidth}\raggedright
Glossary
\end{minipage} \\
\midrule
\endhead
\textbf{branch}: Development branches can be created at any point in time and work on each branch can continue independently.This is useful for testing out new ideas (both code and text) which may or may not eventually get integrated into the main branch of the project. Branches can also be used to isolate contributions of multiple contributors. Each person working on their own branch eliminates problems that arise when conflicting edits are \textbf{pushed} to the same remote branch. Changes in a development branch can be \textbf{merged} into the main branch via \textbf{pull requests}. Branches can only be made by those who are given access to the project \textbf{repository}. \\
\textbf{clone}: Cloning a \textbf{repository} is a way of making a local copy (i.e.~on your computer) of a GitHub \textbf{repository}. If you have access to \textbf{push} to a \textbf{repository}, this can be a first step to contributing to a project. \\
\textbf{commit}: Commits are snapshots of the development of a project. In Git, versions of files and directories are uniquely identified as ``commits'', allowing one to identify and track modifications line-by-line. Commits can include changes in multiple files and must include a brief commit message describing the changes made. A typical workflow is to make some related changes in files, make a commit (e.g.~``generate and include fig1 in results''), and after several commits \textbf{push} those commits to the remote (i.e., cloud-based) GitHub \textbf{repository}. \\
\textbf{fork}: A fork is a copy of a \textbf{repository} hosted on GitHub. If a repository is public, then anyone can make a fork. Even if they do not have access to \textbf{push} to the original repository, they can make a fork and edit it independently. Forks are linked to the original GitHub repository and ``upstream'' changes (those in the original repository) can be \textbf{merged} to keep the fork up to date with the original project. Changes made in the fork can be integrated into the original project via \textbf{pull requests}. \\
\textbf{merge}: Combining \textbf{commits} from two different branches together into one \textbf{branch} \\
\textbf{pull request}: A pull request is a request that the owner(s) of a GitHub repository integrate changes you've made on either a \textbf{branch} in the repository or in your own \textbf{fork}. When you initiate a pull request, you must provide a description of what changes are made. Some automated tests may be run and review may be required before integrating your changes into the main \textbf{branch}. \\
\textbf{push/pull}: When \textbf{commits} are made in a project locally, they must be synced with the remote GitHub repository by \textbf{pushing} them. Changes on a GitHub repository can then be \textbf{pulled} to keep your local version of the project up-to-date. \\
\textbf{repository}: Commonly shortened to ``repo'', a repository is a collection of files (\emph{e.g.}, a directory) tracked by Git. Repositories are managed by an owner and can be listed as ``public'' where the repository will be visible to all GitHub users or ``private'', where the repository is visible only to authorized users. \\
\textbf{release}: At any point a release can be made on GitHub to mark a significant milestone in the progression of a \textbf{repository}. While this GitHub feature is designed with releases of new versions of software in mind (\emph{e.g.}, v1.0.0), it can also be used to create a snapshot of a repository at significant stages like submission, revision, and acceptance of an associated manuscript. \\
\textbf{community}: A forum where GitHub users can ask for advice, offer solutions to questions, and share ideas (https://github.community/). \\
\bottomrule
\end{longtable}

@@

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 0\tabcolsep) * \real{1.0000}}@{}}
\toprule
\begin{minipage}[b]{\linewidth}\raggedright
10 Tips for getting started in GitHub
\end{minipage} \\
\midrule
\endhead
1. \textbf{Check for an existing solution to your problem} The GitHub Help webpage (\url{https://docs.github.com/en}) contains extensive and detailed documents with helpful screenshots. It is a good starting point for handling an issue, and has troubleshooting tips for specific problems. Alternatively, consider Tweeting your issue. There is a large community of GitHub users around the world who have likely faced analogous problems and may be able to provide quick solutions. Third, try to follow blogs (e.g., \url{https://github.blog}), Twitter accounts or YouTube channels that regularly post practical solutions about common GitHub issues. \\
2. \textbf{Consider taking free courses} such as those from Software Carpentries\textsuperscript{\protect\hyperlink{ref-pjy75gHr}{41}} and sharing these courses with your lab members or colleagues. \\
3. \textbf{Take the advantage of GitHub as an asynchronous working tool for team-based projects} See the repository for this paper (\url{https://github.com/SORTEE-Github-Hackathon/manuscript}) as an example of a collaborative manuscript that includes discussions, issues, and a website via GitHub. \\
4. \textbf{The GitHub Learning Lab (\url{https://lab.github.com})} allows you to learn GitHub basics through short projects and tasks, and allows you to get feedback from their Learning Lab bot. \\
5. \textbf{Check out the following markdown cheatsheet (\url{http://markdownguide.org/basic-syntax})} so that you can write clear metadata README files for your repositories. \\
6. \textbf{The Jenny Bryan universe of GitHub material} provides a thorough and accessible introduction for a multitude of research-related uses for GitHub, and includes a book\textsuperscript{\protect\hyperlink{ref-ZvrOcg9w}{42}}, statistics course\textsuperscript{\protect\hyperlink{ref-6CMMeSeD}{43}} and academic article\textsuperscript{\protect\hyperlink{ref-RVetqmsg}{7}}. \\
7. \textbf{Don't be afraid of trial and error} One of the best ways to learn GitHub is the trial and error method. Learning from your own mistakes can be the better way to master your GitHub abilities. In any case, GitHub has the advantage of making it easy to go back to any steps that you desire via version controlling if you make mistakes. \\
8. \textbf{If you are an educator, include lectures on reproducibility and tools for creating reproducible workflows in your curricula}. Some graduate programs now include coursework on course Rmarkdown and GitHub. Getting students started with these tools earlier will prevent the resistance that comes from working with a less reproducible workflow for a longer period of time. \\
9. \textbf{Try to begin committing with GUI (Graphical user interface) tools} like GitHub Desktop (\url{https://desktop.github.com}), git-gui (\url{https://git-scm.com/docs/git-gui}), RStudio (\url{https://www.rstudio.com}), Visual Studio Code (\url{https://code.visualstudio.com}), Atom (\url{https://atom.io}), GitKraken (\url{https://www.gitkraken.com}) tools instead of CLI (Command line interface) tools such as Terminal or Console for more advanced features. \\
10. \textbf{Get help deciphering GitHub Notifications.} Try using tools like Octobox (\url{https://octobox.io}) to disentangle and manage multiple notifications from distinct GitHub projects. \\
\bottomrule
\end{longtable}

@@

\begin{figure}
\hypertarget{fig:github-diagram}{%
\centering
\includegraphics{images/github_diagram.png}
\caption{An overview of the features of a GitHub repository. A) Multi-faceted components allow for code writing, small data storage, manuscript writing, and project management to all be done in one place. B) Issues, Pull Requests, Discussions, and Projects allow for team members to ask for feedback, suggest fixes, discuss related ideas, and keep track of all the moving parts of a project. C) All collaborators on a project can be a part of a single repository, with varying push privileges and responsibilities. D) CONTRIBUTING.md, LICENCE.md, \& README.md files can allow new team members or others wanting to use materials to understand the project components and learn how they can engage with the project and existing team members.}\label{fig:github-diagram}
}
\end{figure}

@@

Multi-tool & GitHub & yes & yes & yes & NA & Broadly limited free version. Advanced features are provided for free to students and education professionals. & A DOI can only be obtained when integrating to other services that can mint DOI (e.g.~Zenodo, OSF). & 100MB per file, 500MB per private repository (2GB for paid accounts). 100GB for public repositories. Larger files (up to 2GB) can be attached to releases & NA \\
Multi-tool & OSF & yes & yes & yes & yes & yes & yes & 25GB for private projects, up to 5GB per file, plus partner add-ons, 50GB for public projects & yes \\

@@

Temporary (personal) drive storage & Google Drive & yes & yes & yes & yes & limited free version \& paid & NA & 15GB free, up to 100GB with Google One & yes \\

@@

Temporary (personal) drive storage & DropBox & limited & yes & yes & yes & limited free version \& paid & NA & 2GB free & yes \\
Temporary (personal) drive storage & OneDrive and the Office Suite & yes & yes & yes & yes & limited free version \& paid & NA & 5 GB free, up to 1TB paid & yes \\

@@

Collaborative code/text editors & Jupyter Notebook & yes & ? & yes & with Colab & yes & NA & via Binder: no hard limit, but suggests no files \textgreater100MB, can also store on GitHub or Google Colab & yes \\

>>>>

This manuscript
(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/c579f2e6dabd3334b02f563bb8ac53bfd042db72/}{permalink})
was automatically generated
from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/c579f2e6dabd3334b02f563bb8ac53bfd042db72}{SORTEE-Github-Hackathon/manuscript@c579f2e}
on June 8, 2022.

@@

  >{\raggedright\arraybackslash}p{(\columnwidth - 0\tabcolsep) * \real{1.0000}}@{}}
Glossary
\textbf{branch}: A git branch is an alternative line of development for a project (repository). Branches allow to add new features or modifications to the project without affecting the main part of the project. Development branches can be created at any point in time and work on each branch can continue independently. Branching is useful for testing out new ideas (both code and text) which may or may not eventually get integrated into the main branch of the project. Branches can also be used to isolate contributions of multiple contributors. Each person working on their own branch eliminates problems that may arise if conflicting edits are \textbf{pushed} to the same remote branch. Changes in a development branch can be \textbf{merged} into the main branch via \textbf{pull requests}. Branches can only be made by those who are given access to the project \textbf{repository}. \\
\textbf{clone}: Cloning a \textbf{repository} is a way of making a local copy (i.e.~on your computer) of a GitHub \textbf{repository}. If you have access to \textbf{push} to a \textbf{repository}, this can be a first step to contributing to a project. \\
\textbf{commit}: Commits are snapshots of the development of a project. In Git, versions of files and directories are uniquely identified as ``commits'', allowing one to identify and track modifications line-by-line. Commits can include changes in multiple files and must include a brief commit message describing the changes made. A typical workflow is to make some related changes in files, add a commit message (e.g.~``generate and include fig1 in results''), and after several commits \textbf{push} those commits to the remote (i.e., cloud-based) GitHub \textbf{repository}. \\
\textbf{fork}: A fork is a copy of a \textbf{repository} hosted on GitHub. If a repository is public, then anyone can make a fork. Even if they do not have access to \textbf{push} to the original repository, they can make a fork and edit it independently. Forks are linked to the original GitHub repository and ``upstream'' changes (i.e.~those in the original repository) can be \textbf{merged} to keep the fork up to date with the original project. Changes made in the fork can be integrated into the original project via \textbf{pull requests}. \\
\textbf{merge}: Combining \textbf{commits} from two different branches together into one \textbf{branch} \\
\textbf{pull request}: A pull request is a request that the owner(s) of a GitHub repository integrate changes you've made on either a \textbf{branch} in the repository or in your own \textbf{fork}. When you initiate a pull request, you must provide a description of what changes were made. Some automated tests may be run and review may be required before integrating your changes into the main \textbf{branch}. \\
\textbf{push/pull}: When \textbf{commits} are made in a project locally, they must be synced with the remote GitHub repository by \textbf{pushing} them. Changes on a GitHub repository can then be \textbf{pulled} to keep your local version of the project up-to-date. \\
\textbf{repository}: Commonly shortened to ``repo'', a repository is a collection of files (\emph{e.g.}, a directory) tracked by Git. Repositories are managed by an owner and can be listed as ``public'' where the repository will be visible to all GitHub users or ``private'', where the repository is visible only to authorized users. \\
\textbf{release}: At any point a release can be made on GitHub to mark a significant milestone in the progression of a \textbf{repository}. While this GitHub feature is designed with releases of new versions of software in mind (\emph{e.g.}, v1.0.0), it can also be used to create a snapshot of a repository at significant stages like submission, revision, and acceptance of an associated manuscript. \\
\textbf{community}: A forum where GitHub users can ask for advice, offer solutions to questions, and share ideas (https://github.community/). \\

@@

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 0\tabcolsep) * \real{1.0000}}@{}}
\toprule
\begin{minipage}[b]{\linewidth}\raggedright
10 Tips for getting started in GitHub
\end{minipage} \\
\midrule
\endhead
1. \textbf{Check for an existing solution to your problem.} The GitHub Help webpage (\url{https://docs.github.com/en}) contains extensive and detailed documents with helpful screenshots. It is a good starting point for handling an issue, and has troubleshooting tips for specific problems. Alternatively, consider Tweeting your issue. There is a large community of GitHub users around the world who have likely faced analogous problems and may be able to provide quick solutions. Third, try to follow blogs (e.g., \url{https://github.blog}), Twitter accounts or YouTube channels that regularly post practical solutions about the most widely-used web platform for common GitHub issues. \\
2. \textbf{Consider taking free courses.} such as those from Software Carpentry\textsuperscript{\protect\hyperlink{ref-pjy75gHr}{41}} and sharing these courses with your lab members or colleagues. \\
3. \textbf{Take advantage of GitHub as an asynchronous working tool for team-based projects.} See the repository for this paper (\url{https://github.com/SORTEE-Github-Hackathon/manuscript}) as an example of a collaborative manuscript that includes discussions, issues, and a website via GitHub. \\
4. \textbf{The GitHub Learning Lab (\url{https://lab.github.com}).} allows you to learn GitHub basics through short projects and tasks, and allows you to get feedback from their Learning Lab bot. \\
5. \textbf{Check out the following markdown cheatsheet (\url{http://markdownguide.org/basic-syntax}).} so that you can write clear metadata README files for your repositories. \\
6. \textbf{The Jenny Bryan universe of GitHub material.} provides a thorough and accessible introduction for a multitude of research-related uses for GitHub, and includes a book\textsuperscript{\protect\hyperlink{ref-ZvrOcg9w}{42}}, statistics course\textsuperscript{\protect\hyperlink{ref-6CMMeSeD}{43}} and academic article\textsuperscript{\protect\hyperlink{ref-RVetqmsg}{7}}. \\
7. \textbf{Don't be afraid of trial and error.} One of the best ways to learn GitHub is the trial and error method. Learning from your own mistakes can be the better way to master your GitHub abilities. In any case, GitHub has the advantage of making it easy to go back to any steps that you desire via version controlling if you make mistakes. \\
8. \textbf{If you are an educator, include lectures on reproducibility and tools for creating reproducible workflows in the curricula.}. Some graduate programs now include coursework on course Rmarkdown and GitHub. Getting students started with these tools earlier will prevent the resistance that comes from working with a less reproducible workflow for a longer period of time. \\
9. \textbf{Try to begin committing with GUI (Graphical user interface) tools.} like GitHub Desktop (\url{https://desktop.github.com}), git-gui (\url{https://git-scm.com/docs/git-gui}), RStudio (\url{https://www.rstudio.com}), Visual Studio Code (\url{https://code.visualstudio.com}), Atom (\url{https://atom.io}), GitKraken (\url{https://www.gitkraken.com}) tools instead of CLI (Command line interface) tools such as Terminal or Console for more advanced features. \\
10. \textbf{Get help deciphering GitHub Notifications.} Try using tools like Octobox (\url{https://octobox.io}) to disentangle and manage multiple notifications from distinct GitHub projects. \\
\bottomrule
\end{longtable}

@@

\begin{figure}
\hypertarget{fig:github-diagram}{%
\centering
\includegraphics{images/github_diagram.png}
\caption{An overview of git's core features. A) Multi-faceted components allow for code writing, small data storage, manuscript writing, and project management to all be done in one place. B) Issues, Pull Requests, Discussions, and Projects allow for team members to ask for feedback, suggest fixes, discuss related ideas, and keep track of all the moving parts of a project. C) All collaborators on a project can be a part of a single repository, with varying push privileges and responsibilities. D) CONTRIBUTING.md, LICENCE.md, \& README.md files can allow new team members or others wanting to use materials to understand the project components and learn how they can engage with the project and existing team members.}\label{fig:github-diagram}
}
\end{figure}

@@

Multi-tool & GitHub & yes & yes & yes & NA & Broadly limited free version. Advanced features are provided for free to students and education professionals. & A DOI can only be obtained when integrating to other services that can mint DOI (e.g.~Zenodo, OSF). & 100 MB per file, 500 MB per private repository (2 GB for paid accounts). 100 GB for public repositories. Larger files (up to 2 GB) can be attached to releases & NA \\
Multi-tool & OSF & yes & yes & yes & yes & yes & yes & 25 GB for private projects, up to 5GB per file, plus partner add-ons, 50GB for public projects & yes \\

@@

Temporary (personal) drive storage & Google Drive & yes & yes & yes & yes & limited free version \& paid & NA & 15 GB free, up to 100 GB with Google One & yes \\

@@

Temporary (personal) drive storage & DropBox & limited & yes & yes & yes & limited free version \& paid & NA & 2 GB free & yes \\
Temporary (personal) drive storage & One Drive and the Office Suite & yes & yes & yes & yes & limited free version \& paid & NA & 5 GB free, up to 1TB paid & yes \\

@@

Collaborative code/text editors & Jupyter Notebook & yes & ? & yes & with Colab & yes & NA & via Binder: no hard limit, but suggests no files \textgreater100 MB, can also store on GitHub or Google Colab & yes \\
